RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
abstract and mapping from constraint types to constraining elements

>>>>

\subsection{Constraining Elements of Constraint Types}

\begin{itemize}
  \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.	
	\item For a constraint types, there can be multiple constraining elements
	\item The validation of each constraining element has to be implemented
	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
\end{itemize}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{lll}
           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
    \\ \midrule

*Subsumption & $\sqsubseteq$ & sub-classes \\
*Class Equivalence & $\equiv$ & equivalent classes \\
*Sub Properties & $\sqsubseteq$ & sub-properties \\
*Property Domain & $\exists$, $\sqsubseteq$ & property domain \\
*Property Range & $\sqsubseteq$, $\forall$ & property range \\
*Inverse Object Properties & inverse & inverse properties \\
%*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
*Symmetric Object Properties & symmetric & symmetric properties \\
%*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
*Asymmetric Object Properties & asymmetric & asymmetric properties \\
%*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
*Reflexive Object Properties & reflexive & reflexive properties \\
%*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive properties \\
Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
Context-Sp. Property Groups & $\sqcap$ & property group \\
Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or of properties \\
Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or of property groups, \\
                                                          && property group \\
Recursive Queries & - & recursive \\
Individual Inequality & $\ne$ & \\
*Equivalent Properties & $\equiv$ & equivalent properties \\
Property Assertions & = or $\ne$ & \\
Data Property Facets & - & XSD or SPARQL constraining facets \\
                        && examples: regex, xsd:pattern, ... \\
Literal Pattern Matching & - & regex or xsd:pattern \\
Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
*Object Property Paths & $\sqsubseteq$ & property paths \\
*Intersection & $\sqcap$ & intersection \\
*Disjunction & $\sqcup$ & disjunction \\
*Negation & $\neg$ & negation \\
*Existential Quantification & $\exists$ & existential quantification \\
*Universal Quantification & $\forall$ & universal quantification \\
*Minimum Unqualified Cardinality & $\geq$ & \\
*Minimum Qualified Cardinality & $\geq$ & \\
*Maximum Unqualified Cardinality & $\leq$ & \\
*Maximum Qualified Cardinality & $\leq$ & \\
*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Transitive Object Properties & $\sqsubseteq$ & transitive properties \\
Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR of properties \\
Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR of property groups \\
                                                                 & & property group \\
Allowed Values & $\sqcup$ & allowed values \\
Not Allowed Values & $\sqcup$, $\neg$ & not allowed values \\
%Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
Literal Ranges & - & xsd:minInclusive \\
               & & xsd:maxInclusive \\
%Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
Negative Literal Ranges & - & xsd:minInclusive \\
                        & & xsd:maxInclusive \\
Required Properties & $\exists$ & required properties \\

    \bottomrule
    \end{tabular}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{lll}
           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
    \\ \midrule

Optional Properties & $\exists$, $\sqsubseteq$ & optional properties \\
Repeatable Properties & $\geq$ & repeatable properties \\
Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
*Individual Equality & = & \\
*Functional Properties & functional & functional properties \\ 
*Inverse-Functional Properties & inverse, functional & inverse functional properties \\
*Value Restrictions & $\exists$ & value restriction \\
*Self Restrictions & $\exists$ & self restriction \\
Primary Key Properties & inverse, functional & keyfor or primary key \\
*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & property range \\
*Class-Sp. Reflexive Object P. & reflexive & reflexive properties \\
Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
  && controlled vocabularies \\
IRI Pattern Matching & - & IRI pattern matching \\
Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
                         & $\leq$ or = or $\ne$ & \\
Ordering & - & ordered properties, \\
            && ordered values \\ 
Validation Levels & - & validation level \\ 
String Operations & - & SPARQL string operations \\ 
  && examples: STRLEN, \\ 
	&& SUBSTR, CONTAINS \\
Context-Specific Valid Classes & - & context-specific valid classes \\
Context-Specific Valid Properties & - & context-specific valid properties \\
Default Values & - & default values \\
Mathematical Operations & - & example: multiplication \\
Language Tag Matching & - & language tag matching \\
Language Tag Cardinality & - & language tag minimum cardinality, \\
                            && language tag maximum cardinality, \\
													  && language tag exact cardinality \\
Whitespace Handling & - & whitespace \\
HTML Handling & - & html \\
Conditional Properties & $\sqsubseteq$ & conditional properties \\
Recommended Properties & - & recommended properties \\
Handle RDF Collections & - & actions on RDF collections \\
Value is Valid for Datatype & - & value is valid for datatype \\
Use Sub-Super Relations in Validation & - & not redundant properties \\
*Cardinality Shortcuts & & optional \& non-repeatable properties, \\
                       & & optional \& repeatable properties, \\
											 & & mandatory \& non-repeatable properties, \\
											 & & mandatory \& repeatable properties \\
Aggregations & - & aggregations \\
                 && e.g., count \\
*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive properties \\
Provenance & - & provenance \\   
Data Model Consistency & - & SPARQL \\    
Structure & - & SPARQL \\  
Labeling and Documentation & - & SPARQL \\   
Vocabulary & - & vocabulary \\  
HTTP URI Scheme Violation & - & HTTP URI scheme violation \\

    \bottomrule
    \end{tabular}
    \end{center}
\end{table}
